Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-16 icde2016/testing.tex
Fixed a typo in nlp section, added opening paragraph to testing section.
Fixed a section number typo and prettified table.
Addressed #4 and #11 of Fei's feedback.

@@

\begin{table}[ht]
\centering
\begin{tabular}{|p{0.48\linewidth}| p{0.24\linewidth}|}
\hline
\textbf{Number of Records} & 31,546\\ \hline
\textbf{Error Rate} & 27.95\% \\ \hline
\textbf{Analysis Speed ($\mu s$)} & 2,245.04 \\ \hline
\textbf{Validation Speed ($\mu s$)} & 1.65 \\ \hline
\textbf{Median Not Null} & 50 \\ \hline
\end{tabular}
\label{tab:mdlstats}
\caption{MDL Parsing Statistics.}
\end{table}

@@

>>>>

%1 what are the questions to answer
%2 setup (machine/code implementation/data) could be one setup per experiment or as a whole if they are identical
%3. how to perform the experiments
%4. what are the observed results
%5. what are the conclusions(discussions) from the results.

For each of the two algorithms described, we want to measure the fraction of candidate date columns that the algorithm is able to recognize. We describe a large training and experimental corpus that we collected, followed by the results of applying each algorithm to that data.

@@

\begin{table}[ht]
\centering
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|p{0.48\linewidth}| p{0.24\linewidth}|}
\hline
\textbf{Number of Records} & 31,546\\ \hline
\textbf{Error Rate} & 27.95\% \\ \hline
\textbf{Analysis Speed ($\mu s$)} & 2,245.04 \\ \hline
\textbf{Validation Speed ($\mu s$)} & 1.65 \\ \hline
\textbf{Median Not Null} & 50 \\ \hline
\end{tabular}
\egroup
\label{tab:mdlstats}
\caption{MDL Parsing Statistics.}
\end{table}

@@

\subsubsection{Production}

Although both algorithms achieved comparable high accuracies in parsing date time strings, we utilized the minimum description length method in the production code of our system. This was primarily due to the fact that the MDL algorithm was written in C++, allowing for higher performance. We believe that NLP version if written in C++ as opposed to Python, would lead to better performance.
